Baseline centering problem

### 2018-12-12 paper/tangotd.tex

Therefore, if $C$ is definite positive, then variant 1 and variant 2 will converge to
the best approximation (in the parametric family $V$) of
\begin{equation}
\hat V_1\deq C^{-1}\transp{\tilde\Delta}\rho R \qquad\text{and}\qquad \hat
V_2\deq \frac12
C^{-1}(\transp{\tilde\Delta}+\transp{\Delta})\rho R
\end{equation}
respectively.
If $\tilde \Delta=\Delta$, then both $\hat V_1$ and $\hat V_2$
are equal to the desired target
$\Delta^{-1}R$.

Let us study how these fixed points approximate the true target
$\Delta^{-1}R$ when $\tilde \Delta \approx \Delta$. First,
\begin{equation}
C=\frac14 \transp{(\tilde \Delta+\Delta)}\rho(\tilde \Delta+\Delta)-\frac14
\transp{(\tilde
\Delta-\Delta)}\rho(\tilde
\Delta-\Delta)
\end{equation}
Therefore, $C$ is definite positive provided
\begin{equation}
\transp{(\tilde
\Delta-\Delta)}\rho(\tilde
\Delta-\Delta)\prec \transp{(\tilde \Delta+\Delta)}\rho(\tilde \Delta+\Delta)
\end{equation}
which is the case when the model $\tilde \Delta$ is close enough
to the true environment $\Delta$ (moreover the left-hand-side is at
second order in the error). Therefore, convergence is guaranteed in a relatively large
zone around $\Delta$. But the method will diverge if $\tilde \Delta$ is
too far from $\Delta$—contrary to double sampling using the model twice,
which always converges to the value function of the model.

>>>>

Therefore, if $C$ is positive definite, then variant 1 and variant 2 will converge to
the best approximation (in the parametric family $V$) of
\begin{equation}
\hat V_1\deq C^{-1}\transp{\tilde\Delta}\rho R \qquad\text{and}\qquad \hat
V_2\deq \frac12
C^{-1}(\transp{\tilde\Delta}+\transp{\Delta})\rho R
\end{equation}
respectively.
If $\tilde \Delta=\Delta$, then both $\hat V_1$ and $\hat V_2$
are equal to the desired target
$\Delta^{-1}R$.

Let us study how these fixed points approximate the true target
$\Delta^{-1}R$ when $\tilde \Delta \approx \Delta$. First,
\begin{equation}
C=\frac14 \transp{(\tilde \Delta+\Delta)}\rho(\tilde \Delta+\Delta)-\frac14
\transp{(\tilde
\Delta-\Delta)}\rho(\tilde
\Delta-\Delta)
\end{equation}
Therefore, $C$ is positive definite provided
\begin{equation}
\transp{(\tilde
\Delta-\Delta)}\rho(\tilde
\Delta-\Delta)\prec \transp{(\tilde \Delta+\Delta)}\rho(\tilde \Delta+\Delta)
\end{equation}
which is the case when the model $\tilde \Delta$ is close enough
to the true environment $\Delta$ (moreover the left-hand-side is at
second order in the error). Therefore, convergence is guaranteed in a relatively large
zone around $\Delta$. But the method will diverge if $\tilde \Delta$ is
too far from $\Delta$—contrary to double sampling using the model twice,
which always converges to the value function of the model.
